### 2011-12-16 paper.tex
End-of-the-day commit, only details added since last commit

\section{Experimental Methods}

>>>>

\section{Experimental Methods}
The measurents are done in a silicon-fabricated microreactor, developed here at CINF (REF!)....

\section{Results}
Several different samples deposited at various diffent sizes and amounts all show the oscillating bahaviour. Repeatability is high regarding running long experiments on a single sample, but very low from sample to sample.

\section{Discussion}
....
